---
title: "Chick growth"
author: "Rena"
date: "12/9/2019"
output: ioslides_presentation
---
```{r library, include=FALSE}
library(dplyr)
library(plotly)

```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r ChickWeight, include=FALSE}
names(ChickWeight)
head(ChickWeight)
day0 <- ChickWeight %>% filter(Time==0)
DietAve <- ChickWeight %>% group_by(Time, Diet) %>% summarise(weightAve=mean(weight)) %>% ungroup()
```
## Background

We are using Checkweight data frame in R to investigate the effect of diet on early Growth of Chicks.
The dataframe contains experimental data with  `r length(unique(ChickWeight$Chick))` chicks seperate into `r length(unique(ChickWeight$Diet))` diet groups, and their weights were recorded upon their growth.

## Chick growth Analysis

Dataset: CheckWeight

- Boxplot for the weight distribution of newborn chicks used for different diet group
- Lineplot for the effect of diet on the growth of chicks.


## Boxplot for the weight distribution of newborn chicks

```{r distribution}
plot_ly(day0, y = ~weight, color = ~Diet, type = "box")
```

## line Plot for Average Chick Growth at Different Diet

```{r growth}
plot_ly(DietAve, x = ~Time, y = ~weightAve, color = ~Diet, type = "scatter", mode = "lines")
```

## Conslusion

Chicks with Diet 4 grow the fastest.